---
output: pdf_document
toc: no
---
```{r loadlibraries, echo=FALSE, warning = FALSE}

library(knitr)
library(pander)
```

```{r createtitle, results='asis', echo=FALSE}

pandoc.header(cat(cat("# ", providername, sep = ""), "Summary of Survey Results", sep = "\n"), level = 1)

```

Thank you for completing the Understanding and Monitoring Funding Streams in Ryan White Clinics Survey. 
Your response to the survey was crucial in providing the HIV/AIDS Bureau (HAB) and policymakers with a better understanding of how the 
Ryan White HIV/AIDS Program (RWHAP) currently provides primary outpatient health care and essential support services to both uninsured 
and underinsured clients. This document summarizes your survey responses compared to other Part C and D grantee/providers that responded 
to the survey.

```{r chartable, results='asis',echo=FALSE}
  set.caption("Patient Centered Medical Home, Health Home, and MCO Participation")
  pandoc.header("Grantee Characteristics", level = 3)
  pandoc.table(p_chars, split.tables = Inf, style = 'multiline', emphasize.strong.rows = 3, justify = c('left', 'left', 'centre'))

```


```{r oamc_table, results='asis', echo=FALSE, warning=FALSE}

if (length(oamc_all[, 1]) > 0) {
  emph_rows <- which(oamc_all$'OAMC Subservices' %in% oamc_headings)
  
  pandoc.header('Utilization Limits/Clinical Requirements and Insurance Coverage, OAMC Subservices', level = 3)
  set.caption('OAMC Subservices')
  pandoc.table(oamc_all, split.tables = Inf, style = 'multiline', 
               emphasize.strong.rows = emph_rows, 
               split.cells = 75,
               justify = c('left', 'centre', 'centre', 'centre', 'centre'))
} 
```

```{r ss_table, results='asis', echo=FALSE, warning=FALSE}

if (length(ss_all[, 1]) > 0) {
  
  pandoc.header('Utilization Limits/Clinical Requirements and Insurance Coverage, Support Services', level = 3)
  set.caption('Support Services')  
  pandoc.table(ss_all, split.tables = Inf, style = 'multiline', 
               split.cells = 75,
               justify = c('left', 'centre', 'centre', 'centre', 'centre'))
}
```

```{r fundingtable, results='asis', echo=FALSE, warning=FALSE}
if (length(funds[, 1]) > 0) {
  pandoc.header('Reported Data on Funding Sources as a Share of Total Dollars', level = 3)
  set.caption('Funding Source Dollar Amounts')
  
  pandoc.table(funds, split.tables = Inf, style = 'multiline', 
             split.cells = 75,
             emphasize.strong.rows = nrow(funds), 
             justify = c('left', 'centre', 'centre', 'centre'))
}
```

```{r trackertable, results = 'asis', echo=FALSE, warning=FALSE}
if (length(tracker[, 1]) > 0) {
  
  pandoc.header('Ability to Use the Ryan White Services Tracker', level = 3)
  
  set.caption('Ryan White Services Tracker')  
  pandoc.table(tracker, split.tables = Inf, style = 'multiline', 
               split.cells = 75,
               justify = c('left', 'centre', 'centre'))
}
```




